Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Revise abstract

  \paragraph*{Background:} \add{The} assembly of \add{next-generation}
  short-read sequencing data can result in a fragmented non-contiguous series
  of genomic sequences. Therefore a common step in a genome project is to join
  neighbouring sequence regions together and fill gaps \remove{in the assembly
  using additional sequences}. This scaffolding step\remove{, however,} is
  non-trivial and requires manually editing large blocks of nucleotide
  sequence. Joining these sequences together also hides the source of each
  region in the final genome sequence. Taken together, these considerations
  may make reproducing or editing an existing genome \change{build}{scaffold}
  difficult.

@@

  \paragraph*{Results:} This software allows a genome \change{scaffold}{build}
  to be defined in terms of the constituent sequences using a relatively simple
  syntax\remove{to define the scaffold}. This syntax further allows unknown
  regions to be \change{defined}{specified} and add additional sequences to
  fill \add{known} gaps in the scaffold. Defining the genome construction in
  a file makes the scaffolding process reproducible and easier to edit
  compared with \add{large} FASTA nucleotide sequences.

>>>>

  \paragraph*{Background:} \add{The} assembly of \add{next-generation}
  short-read sequencing data can result in a fragmented non-contiguous
  \change{series}{set} of genomic sequences. Therefore a common step in
  a genome project is to join neighbouring sequence regions together and fill
  gaps \remove{in the assembly using additional sequences}. This scaffolding
  step\remove{, however,} is non-trivial and requires manually editing large
  blocks of nucleotide sequence. Joining these sequences together also hides
  the source of each region in the final genome sequence. Taken together,
  these considerations may make reproducing or editing an existing genome
  \change{build}{scaffold} difficult.

@@

  \paragraph*{Results:} This software allows a genome \change{scaffold}{build}
  to be defined in terms of the constituent sequences using a relatively simple
  syntax\remove{to define the scaffold}. This syntax further allows unknown
  regions to be \change{defined}{specified} and \remove{add} additional
  sequence to \add{be used} fill \add{known} gaps in the scaffold. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit compared with \add{large} FASTA nucleotide sequences.
